---
title: "GTEx V6"
author: "Yuxin Zou"
date: 2018-12-20
output:
    workflowr::wflow_html:
      code_folding: hide
---

```{r library}
library(mashr)
library(knitr)
library(kableExtra)
library(ggplot2)
library(gridExtra)
```

```{r read data}
gtex <- readRDS(gzcon(url("https://github.com/stephenslab/gtexresults/blob/master/data/MatrixEQTLSumStats.Portable.Z.rds?raw=TRUE")))
missing.tissues <- c(7, 8, 19, 20, 24, 25, 31, 34, 37)
gtex.colors <- read.table("https://github.com/stephenslab/gtexresults/blob/master/data/GTExColors.txt?raw=TRUE", sep = '\t', comment.char = '')[-missing.tissues, 2]
gtex.colors <- as.character(gtex.colors)
gene.names = as.character(read.table('data/gene_names.txt')[,1])
```

The results are from mashr_flashr_pipeline. We include the data driven covariance matrices based on the first three principal components and factors from `flash`.

## Flash model based on effects:

```{r flash EE factors plot}
factors = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EE.flash.model.rds')$factors
par(mfrow = c(2, 3))
for(k in 1:13){
  barplot(factors[,k], col=gtex.colors, names.arg = FALSE, axes = FALSE, main=paste0("Factor ", k))
}
```

## Flash model based on z scores:

```{r flash EZ factors plot}
factors = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EZ.flash.model.rds')$factors
par(mfrow = c(2, 3))
for(k in 1:18){
  barplot(factors[,k], col=gtex.colors, names.arg = FALSE, axes = FALSE, main=paste0("Factor ", k))
}
```

```{r}
# read model
m_simple_EE = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EE.FL_PC3.mash_model_V_simple.rds')
m_simple_EE$result = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EE.FL_PC3.mash_model_V_simple.posterior.rds')
m_simple_EZ = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EZ.FL_PC3.mash_model_V_simple.rds')
m_simple_EZ$result = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EZ.FL_PC3.mash_model_V_simple.posterior.rds')

m_mle_EE = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EE.FL_PC3.mash_model_V_mle.rds')
m_mle_EE$result = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EE.FL_PC3.mash_model_V_mle.posterior.rds')
m_mle_EZ = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EZ.FL_PC3.mash_model_V_mle.rds')
m_mle_EZ$result = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EZ.FL_PC3.mash_model_V_mle.posterior.rds')

m_Vgene_EE_kushal = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EE.FL_PC3.V_corshrink_xcondition_kushal.mash_model.rds')
m_Vgene_EE_kushal$result = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EE.FL_PC3.V_corshrink_xcondition_kushal.posterior.rds')
m_Vgene_EZ_kushal = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EZ.FL_PC3.V_corshrink_xcondition_kushal.mash_model.rds')
m_Vgene_EZ_kushal$result = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EZ.FL_PC3.V_corshrink_xcondition_kushal.posterior.rds')

m_Vgene_EE_nullz = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EE.FL_PC3.V_corshrink_xcondition_nullz.mash_model.rds')
m_Vgene_EE_nullz$result = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EE.FL_PC3.V_corshrink_xcondition_nullz.posterior.rds')
m_Vgene_EZ_nullz = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EZ.FL_PC3.V_corshrink_xcondition_nullz.mash_model.rds')
m_Vgene_EZ_nullz$result = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EZ.FL_PC3.V_corshrink_xcondition_nullz.posterior.rds')

```

## Estimated null cor V

```{r V, fig.align='center', fig.height=8,fig.width=8}
V.simple = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EE.FL_PC3.V_simple.rds')
corrplot::corrplot(V.simple, method='color', type='upper', tl.col="black", tl.srt=45, tl.cex = 0.5, diag = FALSE, col=colorRampPalette(c("blue", "white", "red"))(200), cl.lim = c(-1,1), title = 'Simple', mar=c(0,0,5,0))
# dev.off()

V.mle.EE = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EE.FL_PC3.V_mle.rds')
corrplot::corrplot(V.mle.EE, method='color', type='upper', tl.col="black", tl.srt=45, tl.cex = 0.5, diag = FALSE, col=colorRampPalette(c("blue", "white", "red"))(200), cl.lim = c(-1,1), title = 'MLE EE', mar=c(0,0,5,0))

V.mle.EZ = readRDS('output/GTExV6pipeline/MatrixEQTLSumStats.Portable.Z.EZ.FL_PC3.V_mle.rds')
corrplot::corrplot(V.mle.EZ, method='color', type='upper', tl.col="black", tl.srt=45, tl.cex = 0.5, diag = FALSE, col=colorRampPalette(c("blue", "white", "red"))(200), cl.lim = c(-1,1), title = 'MLE EZ', mar=c(0,0,5,0))
```

## Results

```{r loglikelihood}
logliks = c(get_loglik(m_simple_EE), get_loglik(m_mle_EE), get_loglik(m_Vgene_EE_kushal), get_loglik(m_Vgene_EE_nullz))
logliks_EZ = c(get_loglik(m_simple_EZ), get_loglik(m_mle_EZ), get_loglik(m_Vgene_EZ_kushal), get_loglik(m_Vgene_EZ_nullz))
tmp = cbind(logliks, logliks_EZ)
row.names(tmp) = c('Simple', 'MLE', 'Vgene Kushal', 'Vgene null z')
colnames(tmp) = c('EE', 'EZ')
tmp %>% kable() %>% kable_styling()
```

```{r plot weights, fig.align='center', fig.height=5,fig.width=20}
par(mfrow=c(1,2))
barplot(get_estimated_pi(m_simple_EE), las=2, cex.names = 0.7, main = 'Simple EE')
barplot(get_estimated_pi(m_mle_EE), las=2, cex.names = 0.7, main = 'MLE EE')
barplot(get_estimated_pi(m_Vgene_EE_kushal), las=2, cex.names = 0.7, main = 'V gene specific EE Kushal')
barplot(get_estimated_pi(m_Vgene_EE_nullz), las=2, cex.names = 0.7, main = 'V gene specific EE null z')

barplot(get_estimated_pi(m_simple_EZ), las=2, cex.names = 0.7, main = 'Simple EZ')
barplot(get_estimated_pi(m_mle_EZ), las=2, cex.names = 0.7, main = 'MLE EZ')
barplot(get_estimated_pi(m_Vgene_EZ_kushal), las=2, cex.names = 0.7, main = 'V gene specific EZ Kushal')
barplot(get_estimated_pi(m_Vgene_EZ_nullz), las=2, cex.names = 0.7, main = 'V gene specific EZ null z')
```


Number of significant:
```{r}
numsig_EE = c(length(get_significant_results(m_simple_EE)), 
              length(get_significant_results(m_mle_EE)), 
              length(get_significant_results(m_Vgene_EE_kushal)), 
              length(get_significant_results(m_Vgene_EE_nullz)))
numsig_EZ = c(length(get_significant_results(m_simple_EZ)), 
              length(get_significant_results(m_mle_EZ)),
              length(get_significant_results(m_Vgene_EZ_kushal)),
              length(get_significant_results(m_Vgene_EZ_nullz)))
tmp = cbind(numsig_EE, numsig_EZ)
row.names(tmp) = c('Simple', 'MLE', 'Vgene Kushal', 'Vgene null z')
colnames(tmp) = c('EE', 'EZ')
tmp %>% kable() %>% kable_styling()
```

The gene significant in `simple EZ`, not in `current EZ`:
```{r fig.align='center', fig.width=20, fig.height=20}
ind = setdiff(get_significant_results(m_simple_EZ), get_significant_results(m_mle_EZ))[9]
stronggene = data.frame(gtex$strong.b[ind,])
colnames(stronggene) = 'EffectSize'
stronggene$Group = row.names(stronggene)
stronggene$se = gtex$strong.s[ind,]
p1 = ggplot(stronggene, aes(y = EffectSize, x = Group)) + 
  geom_point(show.legend = FALSE, color=gtex.colors) + coord_flip() + ggtitle(paste0(gene.names[ind], ' raw')) + ylim(c(-1,1)) + geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4, show.legend = FALSE, color=gtex.colors) + 
  theme_bw(base_size=12) + theme(axis.text.y = element_text(colour = gtex.colors, size = 6))

stronggeneSimple = data.frame(m_simple_EZ$result$PosteriorMean[ind,])
colnames(stronggeneSimple) = 'EffectSize'
stronggeneSimple$Group = row.names(stronggeneSimple)
stronggeneSimple$se = m_simple_EZ$result$PosteriorSD[ind,]
p2 = ggplot(stronggeneSimple, aes(y = EffectSize, x = Group)) + 
  geom_point(show.legend = FALSE, color=gtex.colors) + coord_flip() + ggtitle(paste0(gene.names[ind],' Simple EZ')) + ylim(c(-1,1)) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4, show.legend = FALSE, color=gtex.colors) + 
  theme_bw(base_size=12) + theme(axis.text.y = element_text(colour = gtex.colors, size = 6))

stronggeneMLE = data.frame(m_mle_EZ$result$PosteriorMean[ind,])
colnames(stronggeneMLE) = 'EffectSize'
stronggeneMLE$Group = row.names(stronggeneMLE)
stronggeneMLE$se = m_mle_EZ$result$PosteriorSD[ind,]
p3 = ggplot(stronggeneMLE, aes(y = EffectSize, x = Group)) + 
  geom_point(show.legend = FALSE, color=gtex.colors) + ylim(c(-1,1)) + coord_flip() + ggtitle(paste0(gene.names[ind],' MLE EZ')) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4, show.legend = FALSE, color=gtex.colors) + 
  theme_bw(base_size=12) + theme(axis.text.y = element_text(colour = gtex.colors, size = 6))

stronggeneVgeneKushal = data.frame(m_Vgene_EZ_kushal$result$PosteriorMean[ind,])
colnames(stronggeneVgeneKushal) = 'EffectSize'
stronggeneVgeneKushal$Group = row.names(stronggeneVgeneKushal)
stronggeneVgeneKushal$se = m_Vgene_EZ_kushal$result$PosteriorSD[ind,]
p4 = ggplot(stronggeneVgeneKushal, aes(y = EffectSize, x = Group)) + 
  geom_point(show.legend = FALSE, color=gtex.colors) + ylim(c(-1,1)) + coord_flip() + ggtitle(paste0(gene.names[ind],' V gene specific Kushal EZ')) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4, show.legend = FALSE, color=gtex.colors) + 
  theme_bw(base_size=12) + theme(axis.text.y = element_text(colour = gtex.colors, size = 6))

stronggeneVgeneNullZ = data.frame(m_Vgene_EZ_nullz$result$PosteriorMean[ind,])
colnames(stronggeneVgeneNullZ) = 'EffectSize'
stronggeneVgeneNullZ$Group = row.names(stronggeneVgeneNullZ)
stronggeneVgeneNullZ$se = m_Vgene_EZ_nullz$result$PosteriorSD[ind,]
p5 = ggplot(stronggeneVgeneNullZ, aes(y = EffectSize, x = Group)) + 
  geom_point(show.legend = FALSE, color=gtex.colors) + ylim(c(-1,1)) + coord_flip() + ggtitle(paste0(gene.names[ind],' V gene specific Null EZ')) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4, show.legend = FALSE, color=gtex.colors) + 
  theme_bw(base_size=12) + theme(axis.text.y = element_text(colour = gtex.colors, size = 6))

grid.arrange(p1, p2, p3, p4, p5, nrow = 2)
```

The gene `MCPH1 `:
```{r fig.align='center',fig.height=20,fig.width=20}
ind = 13837
stronggene = data.frame(gtex$strong.b[13837,])
colnames(stronggene) = 'EffectSize'
stronggene$Group = row.names(stronggene)
stronggene$se = gtex$strong.s[13837,]
p1 = ggplot(stronggene, aes(y = EffectSize, x = Group)) + 
  geom_point(show.legend = FALSE, color=gtex.colors) + coord_flip() + ggtitle('ENSG00000249898 row') + ylim(c(-1.3,1.1)) + geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4, show.legend = FALSE, color=gtex.colors) + 
  theme_bw(base_size=12) + theme(axis.text.y = element_text(colour = gtex.colors, size = 6))

stronggeneSimple = data.frame(m_simple_EZ$result$PosteriorMean[13837,])
colnames(stronggeneSimple) = 'EffectSize'
stronggeneSimple$Group = row.names(stronggeneSimple)
stronggeneSimple$se = m_simple_EZ$result$PosteriorSD[13837,]
p2 = ggplot(stronggeneSimple, aes(y = EffectSize, x = Group)) + 
  geom_point(show.legend = FALSE, color=gtex.colors) + ylim(c(-1.3,1.1)) + coord_flip() + ggtitle('ENSG00000249898 Simple EZ') + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4, show.legend = FALSE, color=gtex.colors) + 
  theme_bw(base_size=12) + theme(axis.text.y = element_text(colour = gtex.colors, size = 6))

stronggeneMLE = data.frame(m_mle_EZ$result$PosteriorMean[13837,])
colnames(stronggeneMLE) = 'EffectSize'
stronggeneMLE$Group = row.names(stronggeneMLE)
stronggeneMLE$se = m_mle_EZ$result$PosteriorSD[13837,]
p3 = ggplot(stronggeneMLE, aes(y = EffectSize, x = Group)) + 
  geom_point(show.legend = FALSE, color=gtex.colors) + coord_flip() + ggtitle('ENSG00000249898 MLE EZ') + ylim(c(-1.3,1.1)) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4, show.legend = FALSE, color=gtex.colors) + 
  theme_bw(base_size=12) + theme(axis.text.y = element_text(colour = gtex.colors, size = 6))

stronggeneVgeneKushal = data.frame(m_Vgene_EZ_kushal$result$PosteriorMean[ind,])
colnames(stronggeneVgeneKushal) = 'EffectSize'
stronggeneVgeneKushal$Group = row.names(stronggeneVgeneKushal)
stronggeneVgeneKushal$se = m_Vgene_EZ_kushal$result$PosteriorSD[ind,]
p4 = ggplot(stronggeneVgeneKushal, aes(y = EffectSize, x = Group)) + 
  geom_point(show.legend = FALSE, color=gtex.colors) + ylim(c(-1.3,1.1)) + coord_flip() + ggtitle(paste0(gene.names[ind],' V gene specific Kushal EZ')) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4, show.legend = FALSE, color=gtex.colors) + 
  theme_bw(base_size=12) + theme(axis.text.y = element_text(colour = gtex.colors, size = 6))

stronggeneVgeneNullZ = data.frame(m_Vgene_EZ_nullz$result$PosteriorMean[ind,])
colnames(stronggeneVgeneNullZ) = 'EffectSize'
stronggeneVgeneNullZ$Group = row.names(stronggeneVgeneNullZ)
stronggeneVgeneNullZ$se = m_Vgene_EZ_nullz$result$PosteriorSD[ind,]
p5 = ggplot(stronggeneVgeneNullZ, aes(y = EffectSize, x = Group)) + 
  geom_point(show.legend = FALSE, color=gtex.colors) + ylim(c(-1.3,1.1)) + coord_flip() + ggtitle(paste0(gene.names[ind],' V gene specific Null EZ')) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4, show.legend = FALSE, color=gtex.colors) + 
  theme_bw(base_size=12) + theme(axis.text.y = element_text(colour = gtex.colors, size = 6))


grid.arrange(p1, p2, p3, p4, p5, nrow = 2)
```

The gene significant in `V gene specific EZ (null) tissuewide`, not in `mle EZ`:
```{r fig.align='center',fig.height=20,fig.width=20}
ind = setdiff(get_significant_results(m_Vgene_EZ_nullz), get_significant_results(m_mle_EZ))[10]
stronggene = data.frame(gtex$strong.b[ind,])
colnames(stronggene) = 'EffectSize'
stronggene$Group = row.names(stronggene)
stronggene$se = gtex$strong.s[ind,]
p1 = ggplot(stronggene, aes(y = EffectSize, x = Group)) + 
  geom_point(show.legend = FALSE, color=gtex.colors) + coord_flip() + ggtitle(paste0(gene.names[ind],' row')) + ylim(c(-1.3,1.4)) + geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4, show.legend = FALSE, color=gtex.colors) + 
  theme_bw(base_size=12) + theme(axis.text.y = element_text(colour = gtex.colors, size = 6))

stronggeneSimple = data.frame(m_simple_EZ$result$PosteriorMean[ind,])
colnames(stronggeneSimple) = 'EffectSize'
stronggeneSimple$Group = row.names(stronggeneSimple)
stronggeneSimple$se = m_simple_EZ$result$PosteriorSD[ind,]
p2 = ggplot(stronggeneSimple, aes(y = EffectSize, x = Group)) + 
  geom_point(show.legend = FALSE, color=gtex.colors) + ylim(c(-1.3,1.4)) + coord_flip() + ggtitle(paste0(gene.names[ind],' Simple EZ')) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4, show.legend = FALSE, color=gtex.colors) + 
  theme_bw(base_size=12) + theme(axis.text.y = element_text(colour = gtex.colors, size = 6))

stronggeneMLE = data.frame(m_mle_EZ$result$PosteriorMean[ind,])
colnames(stronggeneMLE) = 'EffectSize'
stronggeneMLE$Group = row.names(stronggeneMLE)
stronggeneMLE$se = m_mle_EZ$result$PosteriorSD[ind,]
p3 = ggplot(stronggeneMLE, aes(y = EffectSize, x = Group)) + 
  geom_point(show.legend = FALSE, color=gtex.colors) + coord_flip() + ggtitle(paste0(gene.names[ind],' MLE EZ')) + ylim(c(-1.3,1.4)) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4, show.legend = FALSE, color=gtex.colors) + 
  theme_bw(base_size=12) + theme(axis.text.y = element_text(colour = gtex.colors, size = 6))

stronggeneVgeneKushal = data.frame(m_Vgene_EZ_kushal$result$PosteriorMean[ind,])
colnames(stronggeneVgeneKushal) = 'EffectSize'
stronggeneVgeneKushal$Group = row.names(stronggeneVgeneKushal)
stronggeneVgeneKushal$se = m_Vgene_EZ_kushal$result$PosteriorSD[ind,]
p4 = ggplot(stronggeneVgeneKushal, aes(y = EffectSize, x = Group)) + 
  geom_point(show.legend = FALSE, color=gtex.colors) + ylim(c(-1,1)) + coord_flip() + ggtitle(paste0(gene.names[ind],' V gene specific Kushal EZ')) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4, show.legend = FALSE, color=gtex.colors) + 
  theme_bw(base_size=12) + theme(axis.text.y = element_text(colour = gtex.colors, size = 6))

stronggeneVgeneNullZ = data.frame(m_Vgene_EZ_nullz$result$PosteriorMean[ind,])
colnames(stronggeneVgeneNullZ) = 'EffectSize'
stronggeneVgeneNullZ$Group = row.names(stronggeneVgeneNullZ)
stronggeneVgeneNullZ$se = m_Vgene_EZ_nullz$result$PosteriorSD[ind,]
p5 = ggplot(stronggeneVgeneNullZ, aes(y = EffectSize, x = Group)) + 
  geom_point(show.legend = FALSE, color=gtex.colors) + ylim(c(-1.3,1.4)) + coord_flip() + ggtitle(paste0(gene.names[ind],' V gene specific Null EZ')) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4, show.legend = FALSE, color=gtex.colors) + 
  theme_bw(base_size=12) + theme(axis.text.y = element_text(colour = gtex.colors, size = 6))


grid.arrange(p1, p2, p3, p4, p5, nrow = 2)
```

The pairwise sharing by magnitude
```{r fig.align='center',fig.height=15,fig.width=30}
par(mfrow = c(1,2))
clrs=colorRampPalette(rev(c('darkred', 'red','orange','yellow','cadetblue1', 'cyan', 'dodgerblue4', 'blue','darkorchid1','lightgreen','green', 'forestgreen','darkolivegreen')))(200)

x           <- get_pairwise_sharing(m_simple_EZ)
colnames(x) <- colnames(get_lfsr(m_simple_EZ))
rownames(x) <- colnames(x)

corrplot::corrplot(x, method='color', type='upper', tl.col="black", tl.srt=45, tl.cex = 0.7, diag = FALSE, col=clrs, cl.lim = c(0,1), title = 'Simple EZ', mar=c(0,0,5,0))

x           <- get_pairwise_sharing(m_mle_EZ)
colnames(x) <- colnames(get_lfsr(m_mle_EZ))
rownames(x) <- colnames(x)
corrplot::corrplot(x, method='color', type='upper', tl.col="black", tl.srt=45, tl.cex = 0.7, diag = FALSE, col=clrs, cl.lim = c(0,1), title = 'Current EZ', mar=c(0,0,5,0))
```
```{r fig.align='center',fig.height=15,fig.width=30}
par(mfrow = c(1,2))
clrs=colorRampPalette(rev(c('darkred', 'red','orange','yellow','cadetblue1', 'cyan', 'dodgerblue4', 'blue','darkorchid1','lightgreen','green', 'forestgreen','darkolivegreen')))(200)

x           <- get_pairwise_sharing(m_Vgene_EZ_kushal)
colnames(x) <- colnames(get_lfsr(m_Vgene_EZ_kushal))
rownames(x) <- colnames(x)

corrplot::corrplot(x, method='color', type='upper', tl.col="black", tl.srt=45, tl.cex = 0.7, diag = FALSE, col=clrs, cl.lim = c(0,1), title = 'V gene specific Kushal EZ', mar=c(0,0,5,0))

x           <- get_pairwise_sharing(m_Vgene_EZ_nullz)
colnames(x) <- colnames(get_lfsr(m_Vgene_EZ_nullz))
rownames(x) <- colnames(x)
corrplot::corrplot(x, method='color', type='upper', tl.col="black", tl.srt=45, tl.cex = 0.7, diag = FALSE, col=clrs, cl.lim = c(0,1), title = 'V gene specific Null EZ', mar=c(0,0,5,0))
```
