---
title: "GTEx sexDE Updated data"
author: "Yuxin Zou"
date: 2020-01-15
output:
    workflowr::wflow_html:
      code_folding: hide
---

```{r library}
library(mashr)
library(knitr)
library(kableExtra)
library(ggplot2)
library(gridExtra)
```

```{r read data}
sexde <- readRDS('data/sexde.data.rds')

missing.tissues <- c(7, 24, 25, 31, 40, 43, 49, 51, 52)
gtex.colors <- read.table("https://github.com/stephenslab/gtexresults/blob/master/data/GTExColors.txt?raw=TRUE", sep = '\t', comment.char = '')[-missing.tissues, 2]
gtex.colors <- as.character(gtex.colors)
```

The results are from mashr_flashr_pipeline. We include the data driven covariance matrices based on the first three principal components and factors from `flash`.

## Flash model based on effects:

```{r flash EE factors plot}
factors = readRDS('output/sexde.final/outputEE/sexde.data.EE.flash.model.rds')$factors
par(mfrow = c(2, 3))
for(k in 1:13){
  barplot(factors[,k], col=gtex.colors, names.arg = FALSE, axes = FALSE, main=paste0("Factor ", k))
}
```

## Flash model based on z scores:

```{r flash EZ factors plot}
factors = readRDS('output/sexde.final/outputEZ/sexde.data.EZ.flash.model.rds')$factors
par(mfrow = c(2, 3))
for(k in 1:17){
  barplot(factors[,k], col=gtex.colors, names.arg = FALSE, axes = FALSE, main=paste0("Factor ", k))
}
```

```{r}
# read model
m_mle_EE = readRDS('output/sexde.final/outputEE/sexde.ee.fl_pc3.v_mle.mash_model.rds')
m_mle_EZ = readRDS('output/sexde.final/outputEZ/sexde.ez.fl_pc3.v_mle.mash_model.rds')
```

## Estimated null cor V

```{r V, fig.align='center', fig.height=8,fig.width=8}
V.mle.EE = readRDS('output/sexde.final/outputEE/sexde.data.EE.FL_PC3.V_mle.rds')
corrplot::corrplot(V.mle.EE, method='color', type='upper', tl.col="black", tl.srt=45, tl.cex = 0.5, diag = FALSE, col=colorRampPalette(c("blue", "white", "red"))(200), cl.lim = c(-1,1), title = 'MLE EE', mar=c(0,0,5,0))

V.mle.EZ = readRDS('output/sexde.final/outputEZ/sexde.data.EZ.FL_PC3.V_mle.rds')
corrplot::corrplot(V.mle.EZ, method='color', type='upper', tl.col="black", tl.srt=45, tl.cex = 0.5, diag = FALSE, col=colorRampPalette(c("blue", "white", "red"))(200), cl.lim = c(-1,1), title = 'MLE EZ', mar=c(0,0,5,0))
```

## Results

```{r loglikelihood}
logliks = c(get_loglik(m_mle_EE))
logliks_EZ = c(get_loglik(m_mle_EZ))
tmp = cbind(logliks, logliks_EZ)
row.names(tmp) = c('MLE')
colnames(tmp) = c('EE', 'EZ')
tmp %>% kable() %>% kable_styling()
```

```{r plot weights, fig.align='center', fig.height=5,fig.width=20}
par(mfrow=c(1,2))
barplot(get_estimated_pi(m_mle_EE), las=2, cex.names = 0.7, main = 'MLE EE')

barplot(get_estimated_pi(m_mle_EZ), las=2, cex.names = 0.7, main = 'MLE EZ')
```


Number of significant:
```{r}
numsig_EE = c(length(get_significant_results(m_mle_EE)))
numsig_EZ = c(length(get_significant_results(m_mle_EZ)))
tmp = cbind(numsig_EE, numsig_EZ)
row.names(tmp) = c('MLE')
colnames(tmp) = c('EE', 'EZ')
tmp %>% kable() %>% kable_styling()
```

The pairwise sharing by magnitude
```{r fig.align='center',fig.height=15,fig.width=30}
par(mfrow = c(1,2))
clrs=colorRampPalette(rev(c('darkred', 'red','orange','yellow','cadetblue1', 'cyan', 'dodgerblue4', 'blue','darkorchid1','lightgreen','green', 'forestgreen','darkolivegreen')))(200)

x           <- get_pairwise_sharing(m_mle_EE)
colnames(x) <- colnames(get_lfsr(m_mle_EE))
rownames(x) <- colnames(x)
corrplot::corrplot(x, method='color', type='upper', tl.col="black", tl.srt=45, tl.cex = 0.7, diag = FALSE, col=clrs, cl.lim = c(0,1), title = 'MLE EE', mar=c(0,0,5,0))

x           <- get_pairwise_sharing(m_mle_EZ)
colnames(x) <- colnames(get_lfsr(m_mle_EZ))
rownames(x) <- colnames(x)
corrplot::corrplot(x, method='color', type='upper', tl.col="black", tl.srt=45, tl.cex = 0.7, diag = FALSE, col=clrs, cl.lim = c(0,1), title = 'MLE EZ', mar=c(0,0,5,0))
```

```{r}
meta_result = read.table('data/meta.ivw.sexde_logfc_matrix.sexde.svs.allgenes.v8.FINAL.txt', header = TRUE)
meta_gene = as.character(meta_result$gene[meta_result$padj < 0.05])
meta_gene = sapply(strsplit(meta_gene, '_', fixed = TRUE), function(x) x[1])
length(intersect(meta_gene, names(get_significant_results(m_mle_EZ))))
```

There are 11212 significant genes from meta analysis, 9707 of them are significant in mash model (EZ) as well.

The gene significant in meta analysis, not in `MLE EZ`:
```{r fig.align='center',fig.height=20,fig.width=20}
ind.name = setdiff(meta_gene, names(get_significant_results(m_mle_EZ)))[1]
ind = which(row.names(sexde$random.b) == ind.name)
stronggene = data.frame(sexde$random.b[ind,])
colnames(stronggene) = 'EffectSize'
stronggene$Group = row.names(stronggene)
stronggene$se = sexde$random.s[ind,]
p1 = ggplot(stronggene, aes(y = EffectSize, x = Group)) + 
  geom_point(show.legend = FALSE, color=gtex.colors) + coord_flip() + ggtitle('Row') + ylim(c(-1.6,1.1)) + geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4, show.legend = FALSE, color=gtex.colors) + 
  theme_bw(base_size=12) + theme(axis.text.y = element_text(colour = gtex.colors, size = 6))

stronggeneMLE = data.frame(m_mle_EZ$result$PosteriorMean[ind,])
colnames(stronggeneMLE) = 'EffectSize'
stronggeneMLE$Group = row.names(stronggeneMLE)
stronggeneMLE$se = m_mle_EZ$result$PosteriorSD[ind,]
p2 = ggplot(stronggeneMLE, aes(y = EffectSize, x = Group)) + 
  geom_point(show.legend = FALSE, color=gtex.colors) + coord_flip() + ggtitle('MLE EZ') + ylim(c(-1.6,1.1)) + 
  geom_errorbar(aes(ymin=EffectSize-1.96*se, ymax=EffectSize+1.96*se), width=0.4, show.legend = FALSE, color=gtex.colors) + 
  theme_bw(base_size=12) + theme(axis.text.y = element_text(colour = gtex.colors, size = 6))

grid.arrange(p1, p2, nrow = 1)
```
